\documentclass[a4paper,11pt]{article}

% PACKAGES
\usepackage{fontspec}
\setmainfont{Roboto}[
    Path = ./fonts/roboto/,
    Extension = .ttf,
    UprightFont = *-Regular,
    BoldFont = *-Bold
]
\usepackage{geometry} 
\usepackage{hyperref} 
\usepackage{xcolor}   
\usepackage{titlesec} 
\usepackage{enumitem} 

% PAGE SETUP
\geometry{a4paper, margin=0.5in} 
\pagestyle{empty} 

% LINK COLORING
\definecolor{linkcolor}{rgb}{0.1, 0.4, 0.7} 
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
}

% CUSTOM SECTION FORMATTING
\titleformat{\section}{\large\scshape\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.2ex plus 1ex minus .2ex}{0.8ex plus .2ex}

% CUSTOM LIST FORMATTING
\setlist[itemize]{leftmargin=*, label=\textbullet, itemsep=0.1em, topsep=0.2em}
\setlength{\parindent}{0pt}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge\scshape\bfseries Suraj Kushwaha} \\
    \vspace{1ex}
    {\large Senior Backend Engineer | Product \& Extensibility Platforms} \\
    \vspace{1ex}
    +91 91067 64917 \quad\textbar\quad
    \href{mailto:jobs@surajkuushwaha.com}{jobs@surajkuushwaha.com} \quad\textbar\quad
    \href{https://github.com/surajkuushwaha}{github/surajkuushwaha} \quad\textbar\quad
    \href{https://linkedin.com/in/surajkuushwaha}{linkedin} 
\end{center}

% --- PROFESSIONAL SUMMARY ---
\vspace{1ex}
Product-minded Backend Engineer with over 4+ years of impact (normalized) specializing in scalable Node.js/TypeScript ecosystems. Proven track record in designing public-facing APIs, leading zero-downtime architectural migrations, and building event-driven systems. Expert in navigating the trade-offs of distributed systems while maintaining a deep focus on the end-user experience for content creators and B2B SaaS platforms.

% --- WORK EXPERIENCE ---
\section*{Work Experience}

\textbf{SDE I (Backend \& Infrastructure)} \hfill \textit{JULY 2022 - PRESENT} \\
\textit{CultureX Entertainment Private Limited} \hfill \textit{Gujarat, India}
\begin{itemize}
    \item \textbf{Extensibility \& APIs:} Owned the end-to-end lifecycle of a public-facing microservice, transforming internal tooling into a high-availability API product; managed documentation and versioning for external developers.
    \item \textbf{Architecture Leadership:} Led a strategic migration from multi-database silos to a unified SaaS architecture for 30+ global brands, prioritizing data consistency and zero-downtime delivery.
    \item \textbf{Systems Thinking:} Architected event-driven social listening tools using AWS EventBridge, SQS, and Lambda; implemented idempotent batch processing to handle 10M+ monthly requests with high reliability.
    \item \textbf{Platform Evolution:} Scaled backend infrastructure on AWS (EC2, SQS, Lambda) to support real-time brand tracking, improving system observability and reducing manual debugging effort by 40\%.
    \item \textbf{Collaborative Delivery:} Developed and launched 10+ MVPs for an influencer marketing platform, collaborating across teams to balance rapid feature delivery with clean, long-term abstractions.
    \item \textbf{Engineering Culture:} Influenced team standards through rigorous code reviews and mentoring, advocating for modern TypeScript patterns and performance-first backend design.
\end{itemize}

% --- TECHNICAL SKILLS ---
\section*{Technical Skills}
\textbf{Core Stack:} Node.js, TypeScript, GraphQL, JavaScript (ES6+), Golang. \\
\textbf{Backend \& Data:} Express.js, Hono, MongoDB, PostgreSQL, MySQL, Redis, RESTful APIs, Microservices. \\
\textbf{Cloud \& Infrastructure:} AWS (Lambda, SQS, SNS, EventBridge, S3, EC2), Docker, GitHub Actions, CI/CD. \\
\textbf{AI \& Tooling:} Advanced use of LLMs for debugging, automated documentation, and code refactoring; Linux, Git, Tmux.

% --- PROJECTS & CREATIVE WORK ---
\section*{Projects \& Content Contribution}
\textbf{Open Read (Creator/Developer)} \hfill \href{https://github.com/surajkuushwaha/open-read}{github.com/surajkuushwaha/open-read}
\begin{itemize}
    \item Developed a cross-browser extension (Plasmo, React, TS) to streamline content accessibility, demonstrating a personal stake in the digital content and publishing ecosystem.
    \item Maintained an open-source workflow, managing community feedback and cross-platform compatibility (Chrome/Firefox/Safari).
\end{itemize}

% --- PROFESSIONAL STRENGTHS ---
\section*{Professional Strengths}
\begin{itemize}
    \item \textbf{Remote/Async Native:} Fluent in written communication, providing generous context in pull requests and documentation to drive progress without needing real-time syncs.
    \item \textbf{Pragmatic Performance:} Experienced in measuring and prioritizing performance bottlenecks in high-traffic B2B environments.
\end{itemize}

% --- EDUCATION ---
\section*{Education}
\textbf{Bachelor of Computer Engineering} \hfill \textit{Government Engineering College, Modasa}

\end{document}